\sysfull

### 2017-08-04 paper/paging.tex
Text added describing result on page swaps (needs second iteration)
added a todo

\begin{figure}
	\centering
	%\includegraphics[width=\columnwidth]{figures/}
	\caption{\sys memory virtualization architecture.\todo{Decide if we really need this figure (we already have a lot of figs)}{Brandon}}
	\label{fig:virtualization_architecture}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\subfloat[SRAM Double Buffer Copy]{\includegraphics[width=0.49\columnwidth]{figures/sram-buffer} }
	\subfloat[DMA Copy]{\includegraphics[width=0.49\columnwidth]{figures/dma}}
	\caption{.\todo{Explain HW/SW setup; make fonts larger, unify legends and axes}{Amjad}}
	\label{fig:sram_vs_dma}
\end{figure}

>>>>

%?\begin{figure}
%?	\centering
%?	%\includegraphics[width=\columnwidth]{figures/}
%?	\caption{\sys memory virtualization architecture.\todo{Decide if we really need this figure (we already have a lot of figs)}{Brandon}}
%?	\label{fig:virtualization_architecture}
%?\end{figure}

@@

\begin{figure}[t]
	\centering
	\subfloat[SRAM Double Buffer Copy]{\includegraphics[width=0.49\columnwidth]{figures/sram-buffer} }
	\subfloat[DMA Copy]{\includegraphics[width=0.49\columnwidth]{figures/dma}}
	\caption{.\todo{Explain HW/SW setup; make fonts larger, unify legends and axes.  We only need to show the right side; this figure shows that we operate out of SRAM and page to FRAM; the copying mechanism is peripheral to the main idea.}{Amjad}}
	\label{fig:sram_vs_dma}
\end{figure}
